Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-15 thesis/experiment.tex
Added in Weka version
Describing the algorithms used for machine learning, added refs. Started answering heuristics question.
Refer to items in ARFF file as instances, as they're known in the literature, also reference the manual

  Weka is data mining software which includes tools for classification of data
  sources using a wide variety of machine learning algorithms
  \parencite{Hall:2009p7662}. It supports processing of an input
  Attribute-Relation File Format (ARFF), a file which contains ASCII text
  describing a list of items with common attributes. Items can be given an
  attribute which provides a nominal classification for verification purposes.

@@

The final stage simulation will be run in three phases:

>>>>

  Weka is data mining software which includes tools for classification of data
  sources using a wide variety of machine learning algorithms
  \parencite{Hall:2009p7662,Bouckaert:2010we}. It supports processing of an
  input Attribute-Relation File Format (ARFF), a file which contains ASCII text
  describing a list of items with common attributes known as instances.
  Instances can be given an attribute which provides a nominal classification
  for verification purposes in Weka. Version 3.6.4 of Weka was used for
  classification during this experiment.

@@

The simulation involves three separate phases of equal length, each simulating a
different kind of network traffic:
